
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV

\documentclass[12pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Anu\c{s}c\u{a} }{Armand}
%%\address{246-1002, Gwangmyeongmayrouge Apt. 86, Cheongna lime-ro, Seo-gu, Incheon-si, 404-180, Rep. of KOREA}
\mobile{(+40) 741-211-776} 
%%% Social
\email{anusca.armand@gmail.com}
%\homepage{www.posquit0.com}
%\github{armandanusca}
\linkedin{armandanusca}
%%% Optionals
%%%\position{Software Engineer{\enskip\cdotp\enskip}Security Expert}
%\quote{``Life is an algorithm and our brain is an operating system."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
 {Company Recruitment Team}
 {}
\letterdate{\today}
\lettertitle{Job Application for Software Engineer}
\letteropening{To whom it may concern,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Anu\c{s}c\u{a} Armand ~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
%\cvparagraph{About Me}
I am writing to express my interest in the summer internship program with your Data Science team. I learned about your company through a couple of my friends who are already working there. I have been a customer for several years without even knowing.
I am currently enrolled in BSc Computer Science and will graduate in June 2021. Despite this, I would also be interested in a year-long placement. While I have a comprehensive backend and mathematical background, my emphasis is on machine learning. \\
Furthermore, during high school, I developed a strong background in algorithms by participating in several programming contests at a national level, as the national Olympiad of Informatics, and international level like International Tournament of Young Mathematicians, which started my passion for coding and trained me to work in stressful conditions. Concerning the working environment, I have worked on Unix OS, especially macOS, Windows and a plentiful of IDEs, text editors and organisational tools, especially Google Suite.

%\cvparagraph{Why The Hut Group?}

I feel that this position would be a perfect fit for me. I am a curious, fast learner who understands the responsibility needed. I was interested in several domains, having tried to work in all of them via internships or hackathons, developing my flexibility. The best way to learn for me it is facing practical problems were I feel like I know nothing. An internship with you will increase my learning opportunities giving me the exposure needed to advance my career while using what I have already learned to make an impact even on such a short time.


\\ \newline
%\cvparagraph{Why Me?}
I previously held an internship at Mambu, working on the backend of a banking engine. During that internship, I have worked in an Agile team with a modified version of Scrum which helped me develop teamwork and communication skills. I also learned how to work with a large codebase, what are the most common challenges of this industry and how can I solve them when I invest enough time. The most interesting part of that project was the complex stack involved because of the nature of confidentiality. \\
Moreover, I have previous experience with Python from several hackathons, the most important one being GreatUniHack18, where I won Daktari Monokai challenge. We developed a chatbot based on Messenger API using several Python library using. It helped the users to get medical advice and a fast way to see a doctor by booking or calling one. It supported English and Swahili which utilised NLP. I was in charge of implementing the last part. It was challenging to implement in 24 hours. 
\\ \newline
I would like the opportunity to meet with you to discuss internship or placement opportunities you have available. Please let me know if you have any questions would like to see specific work samples.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
